Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-29 paper/paper.tex
name of subsections

\subsubsection{Content rarity.} 
This heuristic weighs higher rules that use popular strings in content
options. For a given rule \tname{} takes the arithmetic mean of the
popularity scores of each string used in contents in that rule. More
precisely, we calculate the contribution of content rarity with the
following formula:

@@

\subsubsection{Frequency of content modifiers.} As previously
mentioned, \percRulesWithContent\ (=26K/\numrulessuri) of Suricata
rules involve content options. Furthermore, of the 26K rules that use
content options, 13K use HTTP modifiers\Mar{@Lucas, pode dar o numero
  desconsiderando HTTP? Esta parte eh generica.}. \Luc{Posso, mas nessa função nós consideramos apenas os modificadores http.} Content modifiers
serve to indicate what part of a network packet the string mentioned
in the content option should appear. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} states the requirement that the string ``keep-alive''
be present in the header of the message. (A keep-alive connection
attribute indicates that a single TCP connection should remain open
for multiple HTTP requests/responses.)
Figure~\ref{fig:http-header-example} illustrates possible content
options used to match against certain strings that appear in an HTTP
message. A check (resp., cross) mark indicates a match (resp.,
unmatch).

>>>>

\subsubsection{Popularity of content strings.} 
This heuristic weighs higher rules that use popular strings in content
options. For a given rule \tname{} takes the arithmetic mean of the
popularity scores of each string used in contents in that rule. More
precisely, we calculate the contribution of content rarity with the
following formula:

@@

\subsubsection{Popularity of content modifiers.} As previously
mentioned, \percRulesWithContent\ (=26K/\numrulessuri) of Suricata
rules involve content options. Furthermore, of the 26K rules that use
content options, 13K use HTTP modifiers\Mar{@Lucas, pode dar o numero
  desconsiderando HTTP? Esta parte eh generica.}. \Luc{Posso, mas nessa função nós consideramos apenas os modificadores http.} Content modifiers
serve to indicate what part of a network packet the string mentioned
in the content option should appear. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} states the requirement that the string ``keep-alive''
be present in the header of the message. (A keep-alive connection
attribute indicates that a single TCP connection should remain open
for multiple HTTP requests/responses.)
Figure~\ref{fig:http-header-example} illustrates possible content
options used to match against certain strings that appear in an HTTP
message. A check (resp., cross) mark indicates a match (resp.,
unmatch).
